### 2021-02-16 ch06_paper_gpp/paper_gpp.tex
Renamed figures for chapter 06

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{
    ch06_paper_gpp/figs/schematic_steps.pdf}
  \caption{Schematic illustration of our two-step approach. In step 1 an
    emergent constraint by \textcite{Wenzel2016} is used to constrain the
    global mean fractional change in \acf{GPP} over the 21st century.
    Moreover, this constraint is used to rescale two different gridded target
    variables: absolute \acs{GPP} at the end of the \nth{21} century and
    fractional \acs{GPP} change over the \nth{21} century. In step 2, a
    \acl{ML} model is used to constrain these two target variables (step 2a:
    absolute \acs{GPP}; step 2b: fractional \acs{GPP} change) in two
    independent approaches. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:schematic_steps}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=\LargerFigureWidth{}]{
    ch06_paper_gpp/figs/mlr_concept.pdf}
  \caption{Schematic illustration of our \acf{ML} approach to constrain
    projected absolute \acf{GPP} in step 2a. (a) In the training phase of the
    algorithm, the model is fitted to the training data interpolating the
    empirical (non-linear) relationship between two process-oriented
    diagnostics of the past climate $\left\{ x^{(1)}, x^{(2)} \right\}$ and
    (rescaled) future \acs{GPP} (gray surface). The points show the training
    points for the supervised \acs{ML} algorithm, each of them representing a
    single grid cell/month of a single climate model (the different colors
    correspond to different climate models). (b) In the prediction phase,
    observation-based values of the diagnostic (black points) are fed into the
    trained \acs{ML} model to constrain \acs{GPP} for every grid cell/month to
    a value which best agrees with the observations. (c) For an independent
    validation of our method, we use an out-of-sample testing setup based on a
    leave-one-model-out \acl{CV} approach (see
    \cref{subsec:02:model_weighting} for details). The schematic illustration
    of step 2b differs only in the target variable used (fractional \acs{GPP}
    change instead of absolute \acs{GPP}). \AdaptedFrom{Schlund2020}.}
  \label{fig:06:mlr_concept}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \raisebox{5.5mm}{\includegraphics[width=\columnwidth]{
      ch06_paper_gpp/figs/step2a_rmse.pdf}}
    \caption{}
    \label{fig:06:step2a_ml_inference:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{
      ch06_paper_gpp/figs/step2a_global_feature_importance.pdf}
    \caption{}
    \label{fig:06:step2a_ml_inference:b}
  \end{subfigure}
  \caption{(a) Box plot of the \acf{RMSEP} distributions for six different
    statistical models used to predict future absolute \acf{GPP} in step 2a
    using a leave-one-model-out \acl{CV} approach. The distribution for each
    statistical model contains seven elements (black points; one for each
    climate model used as truth) and is represented in the following way: The
    lower and upper limit of the blue boxes correspond to the $25 \unit{\%}$
    and $75 \unit{\%}$ quantiles, respectively. The central line in the box
    shows the median and the black \enquote{x} shows the mean of the
    distribution. The whiskers outside the box represent the range of the
    distribution. Compared to the \acs{CMIP}5 \acf{MMM} and its corresponding
    rescaled version (r\acs{MMM}), the prediction uncertainty measured by the
    mean \acs{RMSEP} is significantly reduced by up to $48 \unit{\%}$ and $39
    \unit{\%}$, respectively, when using other statistical models. Moreover,
    the non-linear \acf{GBRT} models can slightly reduce the mean \acs{RMSEP}
    compared to the linear \acf{LASSO} models by about $2 \unit{\%}$ for
    \acs{GBRT}-1D (using historical \acs{GPP} as single predictor) and $3
    \unit{\%}$ for the full \acs{GBRT} model (using all predictors). (b)
    Relative global feature importance for the different predictors used in
    the \acs{GBRT} model to predict future absolute \acs{GPP} (step 2a). The
    red bars correspond to positive Pearson correlation coefficients between
    all predictors and the target variable. Due to its strong positive linear
    relationship with the future \acs{GPP}, the historical \acs{GPP} is by far
    the most important predictor in the model. A local feature importance map
    using \acf{LIME} is not shown here because \acs{GPP} is the dominant
    predictor for all grid cells. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:step2a_ml_inference}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\LargeFigureWidth{}]{ch06_paper_gpp/figs/1.pdf}
  \caption{Schematic illustration of our two-step approach. In step 1 an
    emergent constraint by \textcite{Wenzel2016} is used to constrain the
    global mean fractional change in \acf{GPP} over the 21st century.
    Moreover, this constraint is used to rescale two different gridded target
    variables: absolute \acs{GPP} at the end of the \nth{21} century and
    fractional \acs{GPP} change over the \nth{21} century. In step 2, a
    \acl{ML} model is used to constrain these two target variables (step 2a:
    absolute \acs{GPP}; step 2b: fractional \acs{GPP} change) in two
    independent approaches. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:schematic_steps}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=\LargerFigureWidth{}]{ch06_paper_gpp/figs/2.pdf}
  \caption{Schematic illustration of our \acf{ML} approach to constrain
    projected absolute \acf{GPP} in step 2a. (a) In the training phase of the
    algorithm, the model is fitted to the training data interpolating the
    empirical (non-linear) relationship between two process-oriented
    diagnostics of the past climate $\left\{ x^{(1)}, x^{(2)} \right\}$ and
    (rescaled) future \acs{GPP} (gray surface). The points show the training
    points for the supervised \acs{ML} algorithm, each of them representing a
    single grid cell/month of a single climate model (the different colors
    correspond to different climate models). (b) In the prediction phase,
    observation-based values of the diagnostic (black points) are fed into the
    trained \acs{ML} model to constrain \acs{GPP} for every grid cell/month to
    a value which best agrees with the observations. (c) For an independent
    validation of our method, we use an out-of-sample testing setup based on a
    leave-one-model-out \acl{CV} approach (see
    \cref{subsec:02:model_weighting} for details). The schematic illustration
    of step 2b differs only in the target variable used (fractional \acs{GPP}
    change instead of absolute \acs{GPP}). \AdaptedFrom{Schlund2020}.}
  \label{fig:06:mlr_concept}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \raisebox{5.5mm}{\includegraphics[width=\columnwidth]{
      ch06_paper_gpp/figs/4a.pdf}}
    \caption{}
    \label{fig:06:step2a_ml_inference:a}
  \end{subfigure}
  ~
  \begin{subfigure}[b]{\SubfigureWidth{}}
    \includegraphics[width=\columnwidth]{ch06_paper_gpp/figs/4b.pdf}
    \caption{}
    \label{fig:06:step2a_ml_inference:b}
  \end{subfigure}
  \caption{(a) Box plot of the \acf{RMSEP} distributions for six different
    statistical models used to predict future absolute \acf{GPP} in step 2a
    using a leave-one-model-out \acl{CV} approach. The distribution for each
    statistical model contains seven elements (black points; one for each
    climate model used as truth) and is represented in the following way: The
    lower and upper limit of the blue boxes correspond to the $25 \unit{\%}$
    and $75 \unit{\%}$ quantiles, respectively. The central line in the box
    shows the median and the black \enquote{x} shows the mean of the
    distribution. The whiskers outside the box represent the range of the
    distribution. Compared to the \acs{CMIP}5 \acf{MMM} and its corresponding
    rescaled version (r\acs{MMM}), the prediction uncertainty measured by the
    mean \acs{RMSEP} is significantly reduced by up to $48 \unit{\%}$ and $39
    \unit{\%}$, respectively, when using other statistical models. Moreover,
    the non-linear \acf{GBRT} models can slightly reduce the mean \acs{RMSEP}
    compared to the linear \acf{LASSO} models by about $2 \unit{\%}$ for
    \acs{GBRT}-1D (using historical \acs{GPP} as single predictor) and $3
    \unit{\%}$ for the full \acs{GBRT} model (using all predictors). (b)
    Relative global feature importance for the different predictors used in
    the \acs{GBRT} model to predict future absolute \acs{GPP} (step 2a). The
    red bars correspond to positive Pearson correlation coefficients between
    all predictors and the target variable. Due to its strong positive linear
    relationship with the future \acs{GPP}, the historical \acs{GPP} is by far
    the most important predictor in the model. A local feature importance map
    using \acf{LIME} is not shown here because \acs{GPP} is the dominant
    predictor for all grid cells. \AdaptedFrom{Schlund2020}.}
  \label{fig:06:step2a_ml_inference}
\end{figure}
